---
title: "Untitled"
author: "grienne"
date: "January 20, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Libraries & Data}

library(foreign)
library(haven)
library(tidyverse)
library(broom)

ventilation_study <- read_sas("ventilation_study.sas7bdat", 
    NULL)

hgb <- read.csv("hgb.csv", header = TRUE)


```


Question 1 (a)

i. 


B-hat = -.3481.
B-hat SE = .408
Df = 46

ii.

The mean difference is -.3481 and is not statistically significant at t = -.853 and p > .05


```{r}

q1_lm <- lm(temperature~vent_volume, data = ventilation_study)
summary(q1_lm)

```

Question 1b

i.B= -1.825821, SE = 3.38882, df = 7

ii. No

iii. No, they are the same.

```{r}


q1_lm_b <- ventilation_study %>%
             group_by(subject) %>%
               do(tidy(lm(temperature~vent_volume, data =.))) 

q1_i <- q1_lm_b %>%
        group_by(subject) %>%
          filter(term != "(Intercept)")

mean(q1_i$estimate)

mean(q1_i$std.error)

t.test(q1_i$estimate, mu = 0)
```



Question 2a. 

i. Mean diff for paired was 2.952809, for non-paired was 2.953; 
   There is a significant difference at p < .05
ii. the 2 sample t test given the CI being smaller. 

```{r}

q2_a1 <- t.test(hgb$hgb9,hgb$hgb36, alternative = "two.sided", paired = FALSE, var.equal = FALSE)
q2_a1

q2_a1_pair<- t.test(hgb$hgb9,hgb$hgb36, paired=TRUE)
q2_a1_pair

```


Question 2b

--There is not a significant difference (p >.05)
--R^2 = .0003

```{r}

q2_b <- lm(change~group, data= hgb)
summary(q2_b)

```


Question 2c

--There is an association (p<.05)
--With increased water consumption, the rate of changed is positively correlated. 
--Confidence Interval (0.003575739, 0.003874455)
--R^2 = .71
--This model has a much higher R-squared and likely more accuracy


```{r}

q2_c <- lm(change~water, data = hgb)
summary(q2_c)

confint(q2_c)
```